---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# pipeline_football_predictions

<!-- badges: start -->
<!-- badges: end -->

The goal of pipeline_football_predictions is to  predict all matches for Germany teams in Bundesliga, Chanpions league and DFB Pokal. The final result is save as a textfile name result.txt. There is also a correlation plot of our variables.

To run this pipeline, you have to clone this repository:

Termial: git clone git@github.com:Franosei/pipeline_football_predictions.git

R studio: Go to New Project $\rightarrow$ Version control $\rightarrow$ Git $\rightarrow$ copy and paste "git@github.com:Franosei/pipeline_football_predictions.git" in the Repository URL  $\rightarrow$ Create Project.

To run this pipeline, you first have to run this 

```{r,warning=FALSE,message=FALSE}
renv::activate
renv::restore()
```

You can now run the pipeline simply with
```{r,warning=FALSE,message=FALSE}
targets::tar_make()
```


