---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# pipeline_football_predictions

<!-- badges: start -->
<!-- badges: end -->

The goal of pipeline_football_predictions is to  predict all matches for Germany teams in Bundesliga, Chanpions league and DFB Pokal. The final result is save as a textfile name result.txt. There is also a correlation plot of our variables.

To run this pipeline, you have to clone this repository:

Termial: git clone git@github.com:Franosei/pipeline_football_predictions.git

R studio: Go to New Project $\rightarrow$ Version control $\rightarrow$ Git $\rightarrow$ copy and paste "git@github.com:Franosei/pipeline_football_predictions.git" in the Repository URL  $\rightarrow$ Create Project.

To run this pipeline, you will need to install the follow package from github and also from CRAN

```{r,warning=FALSE,message=FALSE}
remotes::install_github("Franosei/Football_dataset_package/leagueCR7")
remotes::install_github("Franosei/soccerCR7")
library(leagueCR7)
library(soccerCR7)
library(targets)
library(tidyverse)
library(reshape2)
library(dplyr)
library(ggplot2)
```

You can now run the pipeline simply with
```{r,warning=FALSE,message=FALSE}
targets::tar_make()
```


